---
title: "World of Women MVP"
author: "CharlieDAO NterpriseFT"
output: html_document
---

```{r include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
# prepare env
library(dplyr)
library(reshape)
library(ggplot2)
library(hash)

# loading helper functions
helperFunctionPath <- ('functions/helper_functions/')
sapply(list.files(pattern='[.]R$', path=helperFunctionPath, full.names=TRUE), source)

visualsFunctionsPath <- ('functions/visuals_functions/')
sapply(list.files(pattern='[.]R$', path=visualsFunctionsPath, full.names=TRUE), source)
```

```{r include=FALSE}
# load data
getLatestDataFromGithub()
```

# Update These Values

```{r include=FALSE}
nftName = 'World of Women'
twitterHistory = wow_history
twitterRaw = wow_tweets_primary
```

# Summary Page

-   Social Cards

    -   New Twitter SIdeBar Followers This For Week
    -   Number of Tweets Made
    -   Likes, Retweets, Replies

-   Sales Cards

    -   Number of Sales
    -   Median Sales Price
    -   Rolling Median Sales Price

-   Ownsership Cards

    -   Number of New Owners
    -   Gini Coefficient of Holders
    -   Max, Avg, Median Number Held

-   Executive Summary (Parameterized Paragraph)

Twitter growth was [ABOVE \| BELOW] expected this. There are [\#\#] new followers while [ \#\# ] new followers was expected. Total engagement was [UP \| DOWN] [ %] week over week. The median sales price is [UP \| DOWN] to [\#\#] ETH. With [\#\#] sales this week, Volume is [UP \| DOWN] [%] week over week.

The \# of unique holders is [UP\|DOWN] week over week. The inequality of \# of NFTs owned is [UP \| DOWN] week over week. Your NFT is primarily held alongside [\#1 Competitor] [\#2 competitor][\#3 competitor].

Gas fees averaged [\#\#] gwei over the past week, and sales [OVER \| UNDER]performed relative to gas with [\#\#] sales versus expected [\#\#] given gas fees.

# Social Stats

1.  Twitter Followers over time

    ```{r echo=FALSE}
    createNftTimeSeriesPlot(
      dataframe=twitterHistory,
      dateCol='date',
      outcomeCols='followers',
      nftName=nftName,
      title='Twitter Followers Over Time',
      lowerQuantile=0.00,
      upperQuantile=1.00,
      imputeData=TRUE,
      geomLine=TRUE,
      logScale=FALSE,
      savePlotData=FALSE
    )
    ```

2.  DELTA Twitter Followers over time (vs expected)

3.  Likes/RTs over time

    ```{r echo=FALSE}
    twitterRawSummary <- twitterRaw %>%
      mutate(date = as.Date(primary_tweets.created_at)) %>%
      group_by(date) %>%
      summarise(
        totalLikes = sum(primary_tweets.favorite_count),
        totalRetweets = sum(primary_tweets.retweet_count)
      )

    createNftTimeSeriesPlot(
      dataframe=twitterRawSummary,
      dateCol='date',
      outcomeCols=c('totalLikes', 'totalRetweets'),
      nftName=nftName,
      title='Twitter Engagement Over Time',
      lowerQuantile=0.00,
      upperQuantile=1.00,
      imputeData=TRUE,
      geomLine=TRUE,
      logScale=FALSE,
      savePlotData=FALSE
    )
    ```

4.  Engagement Score over time

5.  Top 3 tweets of the week (vertical on (1) & (2) + Table w/ link \# Owner Stats \# Sales Stats

# Sales Stats (exclude outlier sales)

1.  Rolling median sales price
2.  Sales table
3.  Volume of slaes over time
4.  daily volume and avg gas cost (gwei) per date
5.  any other sales graphs

# Ownership Stats

1.  Number owned boxplot
2.  Top owners table with wallet id and number owned
3.  Number of unique holders over time (derived from sales and transfers)
4.  Gini coefficient over time
5.  NFT Co-occurance in wallets (network)
